
---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}

```

## What People Are Doing on the Train

This report is about observational data collected on train passengers. A response records what they are doing, how old they are estimated to be, and how many stops this observed person stayed for. The idea is to analyze common behaviors on trains and how they vary across different age groups.

```{r}
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRkEp_AR8kTj4erhHn0-UurP3aqrO8iQWXWaiXv3oLXkA___SSceAglezkXc0jtnGURhOBrZ3TNBlTc/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    activity = "What is this person doing while on the train",
    age = "Estimated age group",
    stops = "Number of stops the observed person stayed for (numbers only)"
    
  )

```


A total of **`r nrow(latest_data)`** people were observed.

The shortest trip was **`r min(latest_data$stops)`** stops and the longest was **`r max(latest_data$stops)`** stops.
  



```{r}
ggplot(latest_data, aes(x = age)) +
  geom_bar(fill = "steelblue", colour = "black") +
  labs(
    title = "Age Groups of People Observed on the Train",
    x = "Age Group",
    y = "Number of People"
  )
```

Age Group Analysis

This graph shows the number of people in each age group.  
The **20–30 age group** is the largest, while **50+** is the smallest.  

This suggests that younger individuals may use the train more frequently, possibly due to commuting for work or study.



```{r}
ggplot(latest_data, aes(x = activity, fill = age)) +
  geom_bar(colour = 'black') +
  labs(title = "Activity Distribution by Age Group",
       y = 'Number of people',
       x = 'Activity'
  )
```

Activity Analysis

This graph shows the distribution of activities on the train, grouped by age.  
The **most common activity** is using a phone, particularly among younger age groups.  

This suggests that passengers tend to engage in individual, screen-based activities during their trip.
